Efficient Calculation of Polynomial Features on Sparse Matrices

### 2016-02-13 paper/workshop/sparse_poly.tex
cleaned up intro

\begin{equation}
(x_{i_0}, x_{i_1}, \dots, x_{i_{k-1}}) \rightarrowtail \hspace{-1.9ex} \twoheadrightarrow p_{i_0i_1 \dots i_{k-1}} \in \{0,1,\dots, \binom{D}{k}\} 
\forall (i_0, i_1, \dots, i_{k-1})
\end{equation}
such that $ 0 \le i_0 \le i_1 \le \dots \le i_{k-1} < D$
where $(x_{i_0}, x_{i_1}, \dots, x_{i_{k-1}})$ are column indicies of a row vector $\vec{x}$ of an $N \times D$ input matrix and $p_{i_0i_1 \dots i_{k-1}}$ is a column index of the polynomial expansion matrix.

>>>>

\begin{equation}
(x_{i_0}, x_{i_1}, \dots, x_{i_{k-1}}) \rightarrowtail \hspace{-1.9ex} \twoheadrightarrow p_{i_0i_1 \dots i_{k-1}} \in \{0,1,\dots, \binom{D}{k}\} 
\forall (i_0, i_1, \dots, i_{k-1})
\end{equation}
such that $ 0 \le i_0 \le i_1 \le \dots \le i_{k-1} < D$
where $(x_{i_0}, x_{i_1}, \dots, x_{i_{k-1}})$ are column indicies of a row vector $\vec{x}$ of an $N \times D$ input matrix and $p_{i_0i_1 \dots i_{k-1}}$ is a column index into the polynomial expansion vector for $\vec{x}$.
